Tables

### 2019-11-11 code/figures.rmd
updated tables and figures with ML2 & RRR9/10

#Categorize effects by type of simulation for graphing
effect_type <- distinct(select(dat, effect, effect_type)) %>% 
  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
                                effect_type == "Raw mean difference", "MD", effect_type),
         effect_type = recode(effect_type, "d" = 'SMD',
                              "r" = "Fisher's z"))

@@

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.4)))

@@

Figure 2. Simulated $I^2$  densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 37 effects. Each simulated density consists of approximately 370,000 estimates.

@@

#combined----
combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
#ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
combo
```

>>>>

#Categorize effects by type of simulation for graphing
effect_type <- distinct(select(dat, effect, effect_type)) %>% 
  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
                                effect_type == "Raw mean difference", "MD", effect_type),
         effect_type = recode(effect_type, "d" = 'SMD',
                              "r" = "Fisher's z",
                              "q" = "Cohen's q"))

@@

#combined line plot gives good overview.
ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
  geom_line(alpha = 0.6) +
  theme_bw() +
  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
                     minor_breaks = NULL) +
  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
                     minor_breaks = NULL) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_color_brewer(name = "Effect type", palette = "Dark2", 
                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
  theme(legend.position = c(0.8, 0.4),
        legend.background = element_rect(linetype = "solid", color = "black")) +
  guides(color = guide_legend(override.aes = list(size = 1.4)))

@@

Figure 2. Simulated $I^2$  densities across 67 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 67 effects. Each simulated density consists of approximately 670,000 estimates.

@@

#combined----
combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
# ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
combo
```

### 2019-11-11 code/tables.rmd
updated tables and figures with ML2 & RRR9/10

##Table 1
###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

@@

##Table 2
###Pre-registered multi-lab replication projects
```{r data-summary-table}
#library(dplyr)
#library(kableExtra)

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
Note: For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"

##Table 3
###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

```

@@

het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, $\\\\hat\\\\tau$ = between studies standard deviation, CI = confidence intervals. Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large
heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% 
  landscape()

```

>>>>

## Table 1
### Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
```{r effect-size-heterogeneity-table, cache = TRUE}
#library(kableExtra)
rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
rho <- c(0, .3, .5)
rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")

@@

## Table 2
### Pre-registered multi-lab replication projects
```{r data-summary-table}
#library(dplyr)
#library(kableExtra)

@@

summary.table %>% knitr::kable(booktabs = TRUE,
                               digits = 0,
                               linesep = "\\addlinespace",
                               longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
  column_spec(2, width = "7em") %>% #specify width of paper column 
  column_spec(7, width = "16em") %>% 
  column_spec(8, width = "30em") %>% 
  landscape()
```
Note: For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. N = Participants used for primary analyses by original authors (i.e., after exclusions). RP = Replication Project, K (US) = no. primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report. Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"

## Table 3
### Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
```{r prep-heterogeneity-table, cache = TRUE}
#library(metafor)
#library(dplyr)
#library(purrr)

@@

het$effect <- gsub("&", "\\\\&", het$effect)
```

@@

het %>% knitr::kable(align = "c", longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>% 
  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
  kable_styling(latex_options = c("scale_down", "repeat_header"), font_size = 7) %>% #comment out if outputting html file
  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
  footnote(threeparttable = TRUE, escape = FALSE,
           general = "Effects were estimated in metafor using REML. The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales'. RP = Replication Project, K = no. primary studies, $\\\\hat\\\\tau$ = between studies standard deviation, CI = confidence intervals. Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large
heterogeneity ($I^2$ = 25/50/75\\\\%) respectively. SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation. Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% landscape()
```
